### 2013-11-07 proposal/proposal/chapter1.tex
Changes
changes

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}

%****************************************** END INTRODUCTION****************************************

>>>>

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background 
needed for our research along with the relevant related work. Chapter 3 provides the problem statement and presents our solution model in two 
different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.

### 2013-11-07 proposal/proposal/chapter2.tex
changes

        \begin{figure}
            \begin{center}
            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
            \end{center}
        \end{figure}

@@

    \section{Cooperative Game Theory in Multi-agent Systems}\label{sec:CGTMS}

        \subsection{Cooperative Game Thoery}\label{sec:BRWS}

        \subsection{Motivating Example}\label{sec:CWSDefinition}

@@

        \subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}

@@

@@

Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments. These tools have been utilized in communication networks and service oriented computing literature, where nodes as rational agents try to reason strategically and maximise their benefit.

>>>>

        \begin{figure}
            \begin{center}
%            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \includegraphics[width=16cm]{Figures/community.eps}\label{wsarch}
            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
            \end{center}
        \end{figure}

@@

    \section{Cooperative Game Theory and Multi-agent Systems}\label{sec:CGTMS}

%        Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments. These tools have been utilized in communication networks and service oriented computing literature, where nodes as rational agents try to reason strategically and maximise their benefit.

        Cooperative game is a branch of game theory that studies
        strategies of self-interested entities or agents in a setting
        where those agents can increase their payoff by binding agreements
        and cooperating in groups. We let $N$ be a set of players. Any
        subset $S$ of $N$ can form a group called $coalition$. A
        \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
        a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
        coalition to a real number $v(S)$, the worth of $S$. This number
        usually represents the output or payoff or again the performance
        of these players working together as coalition.  If a coalition
        $S$ is formed, then it can divide its worth, $v(S)$ in any
        possible way among its members. The payoff vector $x \in
        \mathbb{R}^S$ is the amount of payoff being distributed among the
        members of the coalition $S$. The payoff vector satisfies two
        conditions:

        \begin{itemize}
            \item $x_i \geq 0$ for all $i \in N$, and
            \item $\sum_{i \in S} x_i \leq v(S)$
        \end{itemize}

        The second criteria is called the \emph{feasibility} condition,
        according to which, the payoff for each agent cannot be more than
        the coalition total gain. A payoff vector is also \emph{efficient}
        if the payoff obtained by a coalition is distributed amongst the
        coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
        the characteristic function works in \emph{transferable utility}
        (TU) settings, where utility (i.e., payoff) is transferable from
        one player to another, or in other words, players have common
        currency and a unit of income that is worth the same for all players
        \cite{myerson1991game}.

        When dealing with cooperative games, two issues need to be
        addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
        2. How to reward each member when a task is completed?\\
        %
        The following sections help address these two issues.

        \subsection{Cooperative Game Concepts}

            {\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
            v)$, the \emph{Shapley value} of player $i$ is given
            by\cite{shapley_value}:
            \begin{equation}\label{eq:shapley}
            \phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
            \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
            \end{equation}

            \emph{Shapley value} is a unique and fair solution concept for
            payoff distribution among the members of the coalition. It
            basically rewards members with the amount of marginal contribution
            they have to the coalition.

            %\subsubsection{Core}

            {\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
            a coalitional game $(N, v)$ if and only if:
            \begin{equation}\label{eq:core}
            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
            \end{equation}

            The core is basically a set of payoff vectors where no subset of
            players $S^\prime$ could gain more than their current payoff by
            deviating and making their own coalition $\sum_{i \in S^\prime}
            x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
            sub-coalition $S$ is at least as large as the amount that these
            players could earn by forming a coalition by their own. In a
            sense, it is analogue to Nash equilibrium, except that core is
            about deviations from groups of entities. The core is the
            strongest and most popular solution concept in cooperative game
            theory. However, its computation is a combinatorial problem and
            becomes intractable as the number of players increases. The core
            of some real-world problem games may be empty, which means having
            the characteristic function of the game $(N,v)$, there might be no
            possible distribution of payoff assuring stability of subgroups.

            {\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
            characteristic function $v(S)$ is convex if:
            \begin{equation}\label{eq:convex}
            v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
            N.
            \end{equation}

            According to a classic result by Shapley \cite{S1971cores}, convex
            games always have a non-empty core. We will use a variation of
            convexity condition in our algorithm to check whether our
            coalitions are stable.

            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
            %\emph{$\epsilon$-Core:}
            %\\
            When the \emph{core} set of a game is empty, it means no coalition
            of players can gain anything by deviating. An outcome would be
            unstable if a coalition can benefit even by a small amount from
            deviating, which is a strong requirement. In fact, in some
            situations, deviations can be costly, or players may have loyalty
            to their coalitions, or even it can be computationally intractable
            to find those small benefits. It would only make sense for a
            coalition to deviate if the gain from a deviation exceeds the cost
            of performing the deviation. \emph{$\epsilon$-core} relaxes the
            notion of the core, and only requires that no coalition would
            benefit significantly, or within a constant amount($\epsilon$) by
            deviating (see Equation \ref{eq:core}).

            \begin{equation}\label{eq:core2}
            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
            \end{equation}

            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}

            Coalition structure formation is the problem of finding the best
            partition of web services into teams. In these settings, the
            performance of an individual service is less important than the
            \emph{social welfare} of the whole system, which is the sum of the
            values of all teams. Having the game $(N,v)$, a coalition
            structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
            $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
            the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
            CS}v(C)$.
            %The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.

        \subsection{Examples on Cooperative Games}\label{sec:CWSDefinition}

@@

        In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
        is in the core: all coalitions that can produce any output include the landowner, and none of these
        coalitions has any actions that makes her better off than she is in $a_{N}$.

        For any value of n The core contains actions in which the workers receive some output. 
        The workers need the landowner to produce any output, but the landowner
        also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
        workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
        coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
        on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
        coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
         Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
         Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
          $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
          $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
          That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
          is in the core, as you are asked to verify in the following exercise.

%          Core of landowner-worker game: Check that no coalition can improve upon any action of the grand
%          coalition in which the output received by every worker is nonnegative and at most $f(n)-f(n-1)$. (Use the fact that
%          the form of $f$ implies that $f(n)-f(k)\geq (n-k)(f(n)-f(n-1))$ for every $k\leq n$.)

%          We conclude that the core of the game is the set of all actions of the grand coalition in which the output $x_{i}$
%          obtained by each worker $i$ satisfies $0\leq x-{1}\leq f(n)-f(n-1)$ and the output obtained by the landowner is the
%          difference between $f(n)$ and the sum of the worker's shares. In economics jargon, $f(n)-f(n-1)$ is a worker's
%          ``marginal product". Thus in any action in the core, each worker obtains at most her marginal product.

%          The worker's shares of output are driven down to at most $f(n)-f(n-1)$ by competition between coalitions consisting
%          of the landowner and workers, in cahoots with the landowner, can deviate and increase their share of output. That is,
%          each worker's share of output is limited by her comrade's attempts to obtain more output.

%          The fact that each worker's share of output is held down by interworker competition suggests that the workers might
%          be better off if they were to agree not to join deviating coalitions \emph{except as a group}. You are  asked to check
%          this idea in the following exercise.

        %\subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}

@@

        Shapely value is the unique "fair" way to distribute the total surplus generated by the coalition, among all the players.
        The nature of the Shapley value is combinatorial, as all possible orderings to form a
        coalition needs to be considered. This computational complexity can sometimes be
        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
        an increase in payoff of all participants\cite{conf/aaai/YokooCSOI05}. 
        There are some representations that allow to compute the Shapley value efficiently by reducing the input size of the problem.
        One example is \emph{Induced subgraph games}
        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
        their valuation function should be sum of weights all edges between the node and all its neighbors. It is a succinct representation, using
        an adjacency matrix, which need only $O(n^2)$ space to store all the input, which is a big reduction from $O(2^n)$.
        if weights of all the edges in graph are all positive, the Shapley value can be computed in $O(n^2)$ time. 
        However, this representation is not complete, some games cannot be represented by a induced subgraph game\cite{conf/aaai/YokooCSOI05}.

        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set. 
        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
        reducing the overall complexity of the algorithm.

        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer 
        algorithm useful for service orinted computing settings. Our excrements illustrate, these algorithms can provide 
        applicable and near optimal solutions for real world applications.

@@

        % THIS IS REPEATED
        In this research work, we use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.
